---
title: "FML_Assignment_4"
author: "Madhulika"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
# The necessary packages are loaded
library(caret)
```

```{r} 
#install.packages("factoextra")
library(factoextra)
```

```{r}
library(dplyr)
```

```{r}
library(ggplot2)
```

```{r}
library(tidyverse)
```

```{r}
#install.packages("cowplot")
library(cowplot)
```

```{r}
#install.packages("flexclust")
library(flexclust)
```

```{r}
#install.packages("cluster")
library(cluster)
```

```{r}
#install.packages("NbClust")
library(NbClust)
```

```{r}
# It imports the "Pharmaceuticals" dataset from the specified file path
pharma <- read.csv("Pharmaceuticals.csv")
```

```{r}
# The "Pharmacy" dataset will be viewed
view(pharma)
```

```{r}
#  It displays the first few rows of the "Pharmacy" dataset
head(pharma)
```

```{r}
# It displays the summary statistics for the "Pharmacy" dataset
summary(pharma)
```

```{r}
# Calculates the column wise mean of missing values in the "Pharmacy" dataset
colMeans(is.na(pharma))
```

```{r}
# Sets row names of "Pharmacy" to the values in the second column.
row.names(pharma) <- pharma[,2]
# Removes the second column from the "Pharmacy" dataset
pharma <- pharma[,-2]
# Removes the first column and columns 11 to 13 from the updated "Pharmacy" dataset 
pharma_1 <- pharma[,-c(1,11:13)]
```


```{r}
# Checks the dimensions of the "Pharmacy" dataset
dim(pharma)
```

```{r}
# Standardizes the columns of "pharma_1" using the scale function
norm_pharma_1 <- scale(pharma_1)
# Calculates the distance matrix based on the standardized data 
dist <- get_dist(norm_pharma_1)
# Visualizes the distance matrix using function
fviz_dist(dist)
```

```{r}
WSS <- fviz_nbclust(norm_pharma_1, kmeans, method = "wss")
Sil <- fviz_nbclust(norm_pharma_1, kmeans, method = "silhouette")
plot_grid(WSS, Sil)
```

Interpreting the clusters with respect to the numerical variables used in forming the clusters.
# Set the seed for reproducibility
# Performs k-means clustering on the normalized "pharma_1" data with 3 clusters
# Displays the cluster centers 

```{r}
set.seed(123)
kmeans_pharma_opt <- kmeans(norm_pharma_1, centers = 5, nstart = 50)
kmeans_pharma_opt$centers
```

```{r}
# Display the size of each cluster
kmeans_pharma_opt$size
```

```{r}
# Display the within-cluster sum of squares
kmeans_pharma_opt$withinss
```

```{r}
# Visualize the k-means clusters using a scatter plot
fviz_cluster(kmeans_pharma_opt, data = norm_pharma_1)
```

```{r}
set.seed(123)
kmeans_pharma <- kmeans(norm_pharma_1, centers = 3, nstart = 50)
kmeans_pharma$centers
```

```{r}
# Displays the sizes of each cluster obtained from the k-means clustering.
kmeans_pharma$size
```

```{r}
# Displays the within-cluster sum of squares for each cluster
kmeans_pharma$withinss
```

```{r}
# Visualize the k-means clusters using a scatter plot
fviz_cluster(kmeans_pharma, data = norm_pharma_1)
```

```{r}
clusplot(norm_pharma_1,kmeans_pharma$cluster,color = TRUE,shade =TRUE, labels=2,lines=0)
```

```{r}
pharma_2 <- pharma%>% select(c(11,12,13)) %>% mutate(Cluster = kmeans_pharma$cluster)
Med_Recom <- ggplot(pharma_2, mapping = aes(factor(Cluster), fill=Median_Recommendation))+  geom_bar(position = 'dodge') +
labs(x='Clusters', y='Frequence')
Loc <- ggplot(pharma_2, mapping = aes(factor(Cluster), fill=Location)) + geom_bar(position = 'dodge') +
labs(x='Clusters', y='Frequence')
Ex <- ggplot(pharma_2, mapping = aes(factor(Cluster), fill=Exchange)) + geom_bar(position = 'dodge') +
labs(x='Clusters', y='Frequence')
plot_grid(Med_Recom, Loc, Ex)
```

# The chart makes it clear that most companies in cluster 3 are from the United States

#Providing an appropriate name for each cluster using any or all of the variables in the dataset.

Cluster 1 - Global Giants: These companies are considered "overvalued international firms"
Cluster 2 - Growth Prospects: This group is labeled as "growing and leveraged firms" 
Cluster 3 - Stable US Companies: Companies in this cluster are characterized as "mature US firms" 




























